---
title: "Homework 3"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "virids"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1 

Using instacart data 

* exploration of data set

* number of aisles, most ordered items from aisles 

* plotting items ordered 



```{r}
library(p8105.datasets)
data("instacart") 

```

```{r}
instacart %>% 
  count(aisle, name = "ordered_freq") %>% 
  arrange(desc(ordered_freq)) %>% 
  filter(ordered_freq > 10000) %>% 
  mutate(aisle =
           fct_reorder(aisle, ordered_freq)) %>% 
  ggplot(aes(x = aisle, y = ordered_freq, color = aisle)) +
  geom_point() +
  ylim(10000, 160000)+
  coord_flip()
```


There are `r nrow(instacart)` observations in `instacart` and the variables are `r names(instacart)`. All variables are except for `eval_set`, `product_name`, `aisle`, and `department` are class `integer`. The variables named previously are class `character`.
There are 134 aisles represented in `instacart`. Fresh fruits and vegetables are the most ordered items followed by pacakged vegetables and fruits. 

```{r}
instacart %>% 
  filter(aisle == "packaged vegetables fruits")
```



## Need to do:

* give illustrative example of observations

* Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
* Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
* Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

## Problem 2

```{r}
library(p8105.datasets)
data("brfss_smart2010") 
```

```{r}
brfss_smart2010 %>% 
  janitor::clean_names()
```



