---
title: "Homework 3"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "virids"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1 

Using instacart data 

* exploration of data set

* number of aisles, most ordered items from aisles 

* plotting items ordered 



```{r}
library(p8105.datasets)
data("instacart") 

```

Plotting some initial observations


```{r}
instacart %>% 
  count(product_name, name = "count") %>% 
  ggplot(aes(x = product_name, y = count)) + geom_point()
```


```{r}
instacart %>% 
  count(aisle, name = "ordered_freq") %>% 
  arrange(desc(ordered_freq)) %>% 
  filter(ordered_freq > 10000) %>% 
  mutate(aisle =
           fct_reorder(aisle, ordered_freq)) %>% 
  ggplot(aes(x = aisle, y = ordered_freq, color = aisle)) +
  geom_point() +
  ylim(10000, 160000)+
  coord_flip() +
  labs(title = "Orders from grocery aisles", 
       x = "order frequency", 
       y = "aisle name", 
       caption = "Using data from Instacart 2017 dataset to plot the frequency of orders from each aisle")
```


There are `r nrow(instacart)` observations in `instacart` and the variables are `r names(instacart)`. All variables are class `integer` except for `eval_set`, `product_name`, `aisle`, and `department` are class `integer`. The variables named previously are class `character`.
There are 134 aisles represented in `instacart`. Fresh fruits and vegetables are the most ordered items followed by pacakged vegetables and fruits. 

### Making table with 3 most popular items in 3 aisles 

```{r}
pop_products = 
instacart %>% 
  group_by(aisle, product_name) %>% 
   filter(aisle %in% c("packaged vegetables fruits", "dog food care","baking ingredients")) %>%
  summarize(n_obs = n()) %>% 
    arrange(desc(n_obs)) %>% 
   slice(1:3) %>% 
    knitr::kable(digits = 1)
```

Make table showing the mean hour of the day when Pink Lady Apples and Coffee Ice cream are ordered on each day of the week (2 x 7 table)

```{r}
instacart %>% 
  select(product_name, order_hour_of_day, order_dow) %>% 
  filter(product_name == "Coffee Ice Cream" | product_name == "Pink Lady Apples") %>% 
  group_by(product_name, order_dow) %>% 
  summarize(
    mean_hour = mean(order_hour_of_day)
  ) %>% 
  mutate(order_dow = 
    recode(order_dow, 
           "0" = "Monday",
           "1" = "Tuesday",
           "2" = "Wednesday",
           "3" = "Thursday",
           "4" = "Friday",
           "5" = "Saturday",
           "6" = "Sunday")) %>% 
   pivot_wider(
    names_from = order_dow, 
    values_from = mean_hour)
```


## Need to do:

* give illustrative example of observations

* Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.



## Problem 2

Loading brfss data 

```{r}
library(p8105.datasets)
data("brfss_smart2010") 
```

Data cleaning

* Overall health, creating ordered responses "poor" to "excellent"

# Need to do

* how many states observed at 7 or more locations in 2002 and 2010?

```{r}
brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health",
         response == "Excellent" | response == "Very good" | response == "Good" | response == "Fair" | response == "Poor") %>% 
  mutate(response = forcats::fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent"))
  ) %>%
  filter(year == 2002) %>% 
 separate(locationdesc, into = c("state", "county"), convert = TRUE) %>% 
  group_by(state, county) 
```
           


## Problem 3




